\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{float}
\usepackage{csquotes}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Machine Learning-based Spatial Modeling of Sentiment Towards COVID-19\\}

\author{\IEEEauthorblockN{1\textsuperscript{st} Yangxiao Bai}
\IEEEauthorblockA{\textit{Dept. Computer Science} \\
\textit{South Dakota State University}\\
Brookings, South Dakota \\
bai.yangxiao@sdstate.edu}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Abir Mohammad Hadi}
\IEEEauthorblockA{\textit{Dept. Computer Science} \\
\textit{South Dakota State University}\\
Brookings, South Dakota \\
abirmohammad.hadi@sdstate.edu}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Youngsun Jang}
\IEEEauthorblockA{\textit{Dept. Computer Science} \\
\textit{South Dakota State University}\\
Brookings, South Dakota \\
youngsun.jang@sdstate.edu}
}

\maketitle

\begin{abstract}
A variety of efforts have continued over the past two years to cope with the
COVID-19 pandemic. There has been announced an unprecedented rapid vaccine
development, quarantine measures, and economic revival plans by governments,
etc. It will contribute to a more efficient pandemic response to figure out
precisely people's opinions on these measures. This study explores the
possibility of developing a Deep Learning-based system for such a public
sentiment analysis of epidemic-related issues. It is required to utilize some
methods to effectively collect data containing the public opinion to meet
this purpose, and recent advances in machine learning technology have led to
active research utilizing this. In particular, the daily use of social
network services has enabled the researcher to analyze users' emotions using
such advanced technology. Many studies have been conducted in this regard,
but there are relatively few studies focused on the pandemic, and very few
studies have examined dynamic changes over time in specific regions.
Accordingly, our research team conducted a dynamic analysis on sentiment of
Twitter users processing the spatiotemporal data mining. A key part of
spatiotemporal data mining is securing geospatial, temporal, and sentiment
score data from Twitter, which was solved by utilizing IEEE DataPort's
CORONAVIRUS (COVID-19) GEO-TAGED TWEETS DATASET. The Elasticsearch server was
used to perform querying task to refine the data. Furthermore, by configuring
code that can visualize this, we demonstrate the possibility of automatic
data mining and visualization API production in the future. In addition, we
developed a binary classifier capable of predicting positive and negative
emotion classifications of the public by using the decision tree technique of
machine learning with already pre-labeled sentiment score data as input. This
makes it possible to have a dynamic visibility of public sentiment changes on
Covid-related issues by location and time zone. In the long run, this study
plans to conduct sub-topic clustering of Covid-19 Twitter dataset based on
Transfomer which stands on the attention mechanism in the Natural Language
Processin. By analyzing the correlation between the predicted sentiment score
data and the result of sub-topic clustering, we combine spatio-temporal data
mining and deep neural networks. Eventually, this study will contribute to
the better understanding of how sentiments of people change over time along
with detailed topics of pandemic, by different location.
\end{abstract}
\begin{IEEEkeywords}
pandemic, twitter, sentiment, topic clustering, transformer
\end{IEEEkeywords}

\input{sections/introduction}
\input{sections/related}
\input{sections/method}
\input{sections/experiment}
\input{sections/discussion}
\input{sections/conclusion}

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}